The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-13 article.tex
rearranged some things

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent.}
\label{fig:TopicIntr1}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent.}
\label{fig:TopicIntr2}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent. To do so an db\_update message is sent to the central base in order to update the central base's CR table. A request can then be made to obtain the CR table for an individual already registered in the Central base.}
\label{fig:TopicIntr1}
\end{figure}

@@

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent. The messages coming from other agents will come through the message out topic for any ROS node to subscribe to.}
\label{fig:TopicIntr2}
\end{figure}
